\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-20 doc/flexiblesusy-paper.tex
note about internally used SLHAea class and adding reference
add heaviest neutralino to pole mass comparison table to avoid confusion

The standard input and output of the generated spectrum generator is
the SLHA format \cite{Skands:2003cj,Allanach:2008qq}, which is
intended for the communication between MSSM and NMSSM spectrum
generators and observable calculators.  The user has control over the
SLHA block names by editing the SARAH model files and may also add
extra blocks in the \code{FlexibleSUSY.m} model file, as described in
\secref{sec:modfile}.
%
% We use SLHAea \cite{slhaea} to create these SLHA files and with
% simple modifications these can be passed directly to another code
% which uses them as an alternative to writing out the SLHA file.
%
We have tested that the HDECAY $3.4$ \cite{hdecay} and SDECAY $1.4$
\cite{sdecay}, which are shipped with SUSY-HIT \cite{susyhit},
understand the SLHA output of \fs and give matching output to that
from Softsusy.
%
For models which go beyond the MSSM and NMSSM no fixed standard exists
which specifies the spectrum generator input and output format.  For
this reason, \fs allows the user to control the SLHA input and output
blocks in order to simplify the process of passing the output of a
custom \fs-generated spectrum generator to any private or new public
tool developed for that model.

@@

(iii) The pole mass of the lightest neutralino,
$m_{\tilde{\chi}_1^0}$, is given in the third row.  Since the

@@

$4$--$6$.  Since these particles are contained in $6$-plets, the

@@

>>>>

The standard input and output of the generated spectrum generator is
the SLHA format \cite{Skands:2003cj,Allanach:2008qq}, which is
intended for the communication between MSSM and NMSSM spectrum
generators and observable calculators.  The user has control over the
SLHA block names by editing the SARAH model files and may also add
extra blocks in the \code{FlexibleSUSY.m} model file, as described in
\secref{sec:modfile}.
Internally, \fs uses the SLHAea library \cite{slhaea} to read and
write the SLHA files.  The internally stored SLHAea object can be
passed to other programs at the C++ level for inter program
communication.
We have tested that the HDECAY $3.4$ \cite{hdecay} and SDECAY $1.4$
\cite{sdecay}, which are shipped with SUSY-HIT \cite{susyhit},
understand the SLHA output of \fs and give matching output to that
from Softsusy.
%
For models which go beyond the MSSM and NMSSM no fixed standard exists
which specifies the spectrum generator input and output format.  For
this reason, \fs allows the user to control the SLHA input and output
blocks in order to simplify the process of passing the output of a
custom \fs-generated spectrum generator to any private or new public
tool developed for that model.

@@

(iii) The pole masses of the lightest and heaviest neutralinos,
$m_{\tilde{\chi}_1^0}$ and $m_{\tilde{\chi}_4^0}$, are given in the rows
$3$--$4$.  Since the

@@

$5$--$7$.  Since these particles are contained in $6$-plets, the

@@

    $m_{\tilde{\chi}_4^0}$
    & $4181\unit{GeV}$ ($4.17\unit{ms}$)
    & $4174\unit{GeV}$ ($16.1\unit{ms}$)
    & $4174\unit{GeV}$ ($64.2\unit{ms}$) \\
